\ifeng
\subsection*{Participation and presentations at Schools and Conferences}
\else
\subsection*{Participación y presentaciones en Escuelas y Conferencias}
\fi
\noindent
\begin{etaremune}

\item \years{2022} C. Pérez Bertolli, C. Sarmiento-Cano and H. Asorey, \href{https://afan.df.uba.ar/journal/index.php/analesafa/article/view/2300}{Estimación del Flujo de Muones en el Laboratorio Subterráneo ANDES}, ANALES AFA {\textbf{32}} (4) 106--111 (2022) \ifeng Másperi Price 2020 \else Premio Másperi 2020\fi.

\item \years{2022} A.\ Días for the TRACE Collaboration, \href{}{PlomBOX - development of a low-cost CMOS device for environmental monitoring} \en Proceedings of the 17 International Conference on Environmental Science and Technology, 2021, Athens, Greece, \ifeng in press \else en prensa\fi, (2022). \href{http://arxiv.org/abs/2201.03348}{arXiv:2201.03348}[physics.ins-det]

\item \years{2021} A.J.\ Rubio-Montero, R. Pagán-Muñoz, R. Mayo-García, A. Pardo-Diaz, I. Sidelnik, H. Asorey, \href{https://doi.org/10.1109/WSC52266.2021.9715360}{A Novel Cloud-Based Framework For Standardized Simulations In The Latin American Giant Observatory (LAGO)}, \en IEEE Proceedings of the 2021 Winter Simulation Conference (WSC), (2021). \href{http://arxiv.org/abs/2204.02716}{arXiv:2204.02716}[astro-ph.IM]

\item \years{2021} H. Asorey for the MuAr group (A. Almela et al), \href{https://indico.cern.ch/event/1033631/contributions/4530674/}{Muography developments within the MuAR project: advances in simulations and new detectors designs}, \en International Workshop on Cosmic-Ray Muography (Muography2021), Ghent, Belgium, 2021.

\item \years{2021} H. Asorey, R. Calderón-Ardila, R. Mayo-García, L.A.\ Núñez, R. Pagán-Muñoz, A.J.\ Rubio-Montero, C. Sarmiento-Cano, I. Sidelnik, M. Suárez-Durán and A. Taboada, for the LAGO Collaboration, \href{https://ccc.ciencias.uchile.cl/2021colage/abstracts/Hern%C3%A1n%20Asorey.pdf}{Extensive Air Showers Simulations: Applications to Geophysics and Astroparticle Physics}, \en XII Latin American Conference on Space Geophysics (COLAGE 2021), Villarrica, Chile, 2021.

\item \years{2021} A.J.\ Rubio-Montero, R. Pagán-Muñoz, R. Mayo-García, A. Pardo-Diaz, I. Sidelnik, H. Asorey for the LAGO Collaboration, \href{https://doi.org/10.22323/1.395.0261}{The EOSC-Synergy cloud services implementation for the Latin American Giant Observatory (LAGO)}, \en Proc.
37th International Cosmic Ray Conference ICRC2021, PoS(ICRC2021)261, Berlín, Germany, 2021.

\item \years{2021} A. Vásquez Ramírez, M. Ariza Gómez, M. Carrillo Moreno, V. Baldovino Medrano, H. Asorey and L.A. Núñez, \href{https://doi.org/10.22323/1.395.0480}{Improvised Explosive Devices and cosmic rays
}, \en Proc. 37th International Cosmic Ray Conference ICRC2021, PoS(ICRC2021)480, Berlín, Germany, 2021.

\item \years{2021} L. Otiniano, H. Asorey, C. Sarmiento-Cano, I. Sidelnik and M. Suárez-Duran for the LAGO Collaboration, \href{https://doi.org/10.22323/1.395.0267}{Simultaneous particles influence on the LAGO’s Water Cherenkov Detectors signals}, \en Proc.
37th International Cosmic Ray Conference ICRC2021, PoS(ICRC2021)267, Berlín, Germany, 2021.

\item \years{2021} R de Leon-Barrios, J Peña-Rodríguez, JD Sanabria-Gómez, A Vásquez-Ramírez, R Calderón-Ardila, C Sarmiento-Cano, A Vesga-Ramirez, D Sierra-Porta, M Suárez-Durán, H Asorey, Luis A Núñez \href{https://doi.org/10.22323/1.395.0280}{Muography for the Colombian Volcanoes}, \en Proc.
37th International Cosmic Ray Conference ICRC2021, PoS(ICRC2021)280, Berlín, Germany, 2021.

\item \years{2021} J Peña-Rodríguez, R de León-Barrios, A Ramírez-Muñóz, D Villabona-Ardila, M Suárez-Durán, A Vásquez-Ramírez, H Asorey, LA Núñez, \href{https://doi.org/10.22323/1.395.0400}{Muography background sources: simulation, characterization, and machine-learning rejection}, \en Proc.
37th International Cosmic Ray Conference ICRC2021, PoS(ICRC2021)400, Berlín, Germany, 2021.

\item \years{2021} C. Sarmiento-Cano, H. Asorey, J. Sacahui, L. Otiniano, I. Sidelnik for the LAGO Collaboration, \href{https://doi.org/10.22323/1.395.0929}{The Latin American Giant Observatory (LAGO) capabilities for detecting Gamma Ray Bursts}, \en Proc.
37th International Cosmic Ray Conference ICRC2021, PoS(ICRC2021)929, Berlín, Germany, 2021.

\item \years{2021} N.A.\ Santos, S. Dasso, A.M.\ Gulisano, O. Areso, M. Pereira and H. Asorey for the LAGO Collaboration, \href{https://doi.org/10.22323/1.395.304}{Observations of the cosmic ray detector at the Argentine Marambio base in the Antarctic Peninsula}, \en Proc.
37th International Cosmic Ray Conference ICRC2021, PoS(ICRC2021)304, Berlín, Germany, 2021.

\item \years{2021} L.A.\ Núñez, R. De León Barrios, J. Peña-Rodríguez, J. Sanabria-Gómez, A. Vázquez, H. Asorey, C. Sarmiento-Cano, R. Calderón-Ardila, M. Suárez-Durán, A. Vezga-Ramírez, \href{https://ui.adsabs.harvard.edu/abs/2021AGUFMNS25A0419N}{Muography and Colombian Volcanoes} \in Proc. of the 2021 AGU Fall Meetings, NS25A-0419 (2021).

\item \years{2020} J. Peña-Rodríguez, L.A.\ Núñez, H. Asorey, \href{https://doi.org/10.22323/1.390.0984}{Characterization of the muography background using the Muon Telescope (MuTe)}, \en Proc.
40th International Conference on High Energy physics (ICHEP2020), PoS(ICHEP2020)984, Prague,  Czech Republic, 2020. \href{http://arxiv.org/abs/2102.11483}{arXiv:2102.11483}[hep-ex]

\item \years{2020} R. Calderón-Ardila, A Vesga-Ramírez, C Pérez-Bertolli, A Almela, C Sarmiento-Cano, A Taboada, A Sedoski, C Varela, M Gómez, M Gómez-Berisso, H Asorey, \href{https://ui.adsabs.harvard.edu/abs/2020AGUFMNS0130015C/abstract}{Muography Applications in Argentina}, American Geophysical Union Fall Meeting Abstracts, NS013-0015 (2020)

\item \years{2020} R. Calderón-Ardila, H. Asorey, A. Almela, \href{https://doi.org/10.33414/ajea.5.758.2020}{Desarrollo de Técnicas de Muongrafía para Estudios Densitométricos de Objetos de Importancia Estratégica}, AJEA {\textbf{5}} 758 (2020)

\item \years{2020} H. Asorey \ifeng for the TRACE Collaboration \else para la Colaboración TRACE\fi, PlomBOX: Un dispositivo para combatir la contaminación por plomo en agua potable, \ifeng Invited Talk to the Technology and Industry Division of the Argentinian Physics Association, 105th Annual Meeting of the Argentinian Physics Association, Córdoba, Argentina, 2020 \else Charla Invitada en la División de Industria y Tecnología de la Asociación de Física Argentina, presentada en la 105º Reunión Anual de la Asociación de Física Argentina, Córdoba, Argentina, 2020.\fi

\item \years{2019} The LAGO Collaboration, \href{https://arxiv.org/abs/1909.10039}{Contributions of the LAGO Collaboration to the 36th ICRC}, \en Proc.
36th International Cosmic Ray Conference, PoS(ICRC2019)358, Madison, USA, 2019.\\ \href{http://arxiv.org/abs/1909.10039}{arXiv:1909.10039}[physics.astro-ph]

\item \years{2019} Jesús Peña-Rodríguez, Adriana Vásquez-Ramírez, José D Sanabria-Gómez, Luis A Núñez, David Sierra-Porta and Hernán Asorey, \href{https://pos.sissa.it/358/381/}{Calibration and first measurements of MuTe: a hybrid Muon Telescope for geological structures}, \en Proc.
36th International Cosmic Ray Conference, PoS(ICRC2019)358 381, Madison, USA, 2019. \href{http://arxiv.org/abs/1909.09732}{arXiv:1909.09732}[physics.ins-det]

\item \years{2018} Participante en el I Simposio Argentino de Radiocirugía AAR 2018, Universidad de Buenos Aires, Agosto 2018. 

\item \years{2018} H. Asorey, R. Calderón-Ardila, L.A.\ Núñez, J. Peña-Rodríguez, J. Pisco, J.D.\ Sanabria Gómez, C. Sarmiento-Cano, D. Sierra-Porta, M. Suárez-Durán, A. Vásquez-Ramírez \href{}{{Cosmic Rays and Inner Structure of Colombian Volcanoes}} \en Proc.
XI Latin American Conference on Space Geophysics (XI COLAGE), Buenos Aires, Argentina %, Adv. in Space Research, \ifeng in preparación \else under preparation \fi (2018). %\href{http://arxiv.org/abs/1704.04967}{arXiv:1704.04967}[physics.geo-ph]

\item \years{2018} M. Suárez-Durán, H. Asorey, S. Dasso, L.A.\ Núñez \href{}{{Assessing the Geomagnetic Field Contribution During Three Forbush Decreases: May 2005, December 2006 and September 2017 at the Pierre Auger Observatory}} \en Proc.
XI Latin American Conference on Space Geophysics (XI COLAGE), Buenos Aires, Argentina %, Adv. in Space Research, \ifeng in preparación \else under preparation \fi (2018). %\href{http://arxiv.org/abs/1704.04967}{arXiv:1704.04967}[physics.geo-ph]

\item \years{2018} N. Guarín, H. Asorey, I. Sidelnik, M. Suárez-Durán, F. Alcalde, L.H.\ Arnaldi, J. Lipovetzky, M. Pérez, M. Sofo Haro, J.J.\ Blóstein, M. Gómez Berisso, \href{}{{Simulation of Water Cherenkov Detector for neutron detection using Geant4}} \en Proc.
XI Latin American Conference on Space Geophysics (XI COLAGE),  Buenos Aires, Argentina %, Adv. in Space Research, \ifeng in preparación \else under preparation \fi (2018). %\href{http://arxiv.org/abs/1704.04967}{arXiv:1704.04967}[physics.geo-ph]

\item \years{2018} I. Sidelnik, H. Asorey, N. Guarín, F. Alcalde, L.H.\ Arnaldi, J. Lipovetzky, M. Pérez, M. Sofo Haro, M. Gómez Berisso, J.J.\ Blostein \href{}{{Neutron Detection Capabilities of Water Cherenkov Detectors}} \en Proc.
XI Latin American Conference on Space Geophysics (XI COLAGE),  Buenos Aires, Argentina%, Adv. in Space Research, \ifeng in preparación \else under preparation \fi (2018). %\href{http://arxiv.org/abs/1704.04967}{arXiv:1704.04967}[physics.geo-ph]

\item \years{2018} A.M.\ Gulisano, S. Dasso, O. Areso, M. Ramelli, M. Pereira, U. Hereñú, H. Asorey, V.E.\ López, H. Ochoa, F. Iza, for the LAGO Collaboration, \href{}{{Antarctic Node of the Latin American Giant Observatory for Cosmic Rays Observations}} \en Proc.
XI Latin American Conference on Space Geophysics (XI COLAGE),  Buenos Aires, Argentina, Adv.
in Space Research, \ifeng in preparación \else under preparation \fi (2018). %\href{http://arxiv.org/abs/1704.04967}{arXiv:1704.04967}[physics.geo-ph]
	
% DE AQUI PARA ABAJO ESTAN EN EL SIGEVA %%%%
\item \years{2017} Participante en el Simposio Internacional \lq\lq{}Inmunoterapia: La Revolución en el Tratamiento del Cáncer\rq\rq{}, Universidad de Buenos Aires, Noviembre 2017.

\item \years{2017} Participante en la 7ma Conferencia InterAmericana de Oncología ``Estado Actual y Futuro de las Terapias Antioneoplásicas Dirigidas'', Buenos Aires, Octubre 2017. 

\item \years{2017} H. Asorey, A. Jaimes-Motta, L. A. Núñez, J. Peña-Rodríguez, C. Sarmiento-Cano and M. Súarez-Duran for the LAGO Collaboration, \href{http://www.astroscu.unam.mx/rmaa/RMxAC..49/PDF/RMxAC..49\_poster3.pdf}{{The Calibration of the GUANE Array: Extensive Air Showers Reconstruction and Space Weather Studies}} \en Proc.
XV Latin American Regional IAU Meeting LARIM2016, Cartagena, Colombia, Rev.
Mex.
AA, {\textbf{49}} 145--145 (2017)

\item \years{2017} H. Asorey, A. Balaguera-Rojas, A. Martínez-Méndez, L. A. Núñez, J. Peña-Rodríguez, P. Salgado-Meza, C. Sarmiento-Cano and M. Súarez-Duran, \href{http://www.astroscu.unam.mx/rmaa/RMxAC..49/PDF/RMxAC..49\_poster2.pdf}{{Astroclimate: A citizen Science Climate Awareness}} \en Proc.
XV Latin American Regional IAU Meeting LARIM2016, Cartagena, Colombia, Rev.
Mex.
AA, {\textbf{49}} 144--144 (2017)

\item \years{2017} H. Asorey, A. Balaguera-Rojas, R. Calderón Ardila, L. A. Núñez, J. D. Sanabria-Gómez, M. Súarez-Duran and A. Tapia, \href{http://www.astroscu.unam.mx/rmaa/RMxAC..49/PDF/RMxAC..49\_poster2.pdf}{{Muon Telescope (MUTE): A first study using Geant4}} \en Proc.
XV Latin American Regional IAU Meeting LARIM2016, Cartagena, Colombia, Rev.
Mex.
AA, {\textbf{49}} 144--144 (2017)

\item \years{2017} H. Asorey, L. A. Núñez and M. Súarez-Duran, \href{http://www.astroscu.unam.mx/rmaa/RMxAC..49/PDF/RMxAC..49\_oral6.pdf}{{A Simulation Chain for the LAGO Space Weather Program}} \en Proc.
XV Latin American Regional IAU Meeting LARIM2016, Cartagena, Colombia, Rev.
Mex.
AA, {\textbf{49}} 56--56 (2017) \href{http://arxiv.org/abs/1704.07681}{arXiv:1704.07681}[physics.space-ph]

\item \years{2017} H. Asorey, A. Balaguera-Rojas, L. A. Núñez, J. D. Sanabria-Gómez, C. Sarmiento-Cano, M. Súarez-Duran, M. Valencia-Otero, and A. Vesga-Ramírez, \href{http://www.astroscu.unam.mx/rmaa/RMxAC..49/PDF/RMxAC..49\_oral4.pdf}{{Astroparticle Techniques: Colombia active volcano candidates for Muon Telescope}} \en Proc.
XV Latin American Regional IAU Meeting LARIM2016, Cartagena, Colombia, Rev.
Mex.
AA, {\textbf{49}} 54--54 (2017) \href{http://arxiv.org/abs/1704.04967}{arXiv:1704.04967}[physics.geo-ph]

\item \years{2017}H. Asorey, A. Martínez-Méndez, L. A. Núñez and A. Valbuena-Delgado, \href{http://www.astroscu.unam.mx/rmaa/RMxAC..49/PDF/RMxAC..49\_oral5.pdf}{{LAGO Distributed Network Of Data Repositories}} \en Proc.
XV Latin American Regional IAU Meeting LARIM2016, Cartagena, Colombia, Rev.
Mex.
AA {\textbf{49}} 55--55 (2017) \href{http://arxiv.org/abs/1704.03885}{arXiv:1704.03885}[cs.DL]

\item \years{2017}H. Asorey, L. Núñez, C. Y. Pérez Arias, S. Pinilla, F. Quiñonez and M. Suárez-Durán, \href{http://www.astroscu.unam.mx/rmaa/RMxAC..49/PDF/RMxAC..49\_oral7.pdf}{{Astroparticle Techniques: Simulating Cosmic Rays induced Background Radiation on Aircrafts}} \en Proc.
XV Latin American Regional IAU Meeting LARIM2016, Cartagena, Colombia, Rev.
Mex.
AA, {\textbf{49}} 57--57 (2017) \href{http://arxiv.org/abs/1704.03419}{arXiv:1704.03419}[physics.space-ph]

\item \years{2017} H. Asorey, \href{http://ifa.uv.cl/rayoscosmicos/}{{Instructor invitado para la Primera Escuela Chilena de Rayos Cósmicos - IV Escuela ``Astropartículas en LAGO''}}, con el curso \href{https://github.com/lagoproject/astroparticulas}{{``Física de Astropartículas: física, simulaciones y análisis de datos''}}, Universidad de Valparaiso y Universidad de La Serena, Valparaiso y La Serena, Chile (2017).

\item \years{2016} H. Asorey, \href{https://fisica.cab.cnea.gov.ar/jab2016/}{{Instructor invitado para la Escuela Jose Antonio Balseiro 2016: `` Nuevas Tendencias de Investigación en Física Médica''}}, con el curso \href{ https://github.com/asoreyh/intro-nuclear-fisica-medica }{{``Curso de Introducción a Física de Partículas, Nuclear, Aceleradores y Detectores''}}, Instituto Balseiro, San Carlos de Bariloche, Argentina (2016).

\item \years{2016} H. Asorey, R. Mayo-García, L.A.\ Núñez, M. Rodríguez-Pascual, A. J. Rubio-Montero, M. Suarez Durán, and L.A.\ Torres-Niño for the LAGO Collaboration, {{\href{http://dx.doi.org/10.1109/CCGrid.2016.110}{The Latin American Giant Observatory: a successful collaboration in Latin America based on Cosmic Rays and computer science domains}}}, \en Proc.
2016--16th IEEE/ACM International Symposium on Cluster, Cloud and Grid Computing (CCGrid), IEEE Proceedings, pp 707--711, Cartagena, Colombia, 2016, \href{http://arxiv.org/abs/1605.09295}{arXiv:1605.09295}[astro-ph.IM]

\item \years{2015} I. Sidelnik, H. Asorey, J. J. Blostein, M. Gómez Berisso, H. Arnaldi, M. Sofo Haro, {{Detección de Neutrones mediante efecto Cherenkov en Agua}}, Actas de la Reunión Anual de la Asociación Argentina de Tecnología Nuclear (2015).

\item \years{2015}H. Asorey and L. A. Núñez, {{Astroparticle Physics at Eastern Colombia}}, \en Proc.
César Lattes Meeting, \ifeng accepted \else aceptado,\fi Niterói, Brazil, 2015 \href{http://arxiv.org/abs/1510.01305}{arXiv:1510.01305}[astro-ph.IM]

\item \years{2015}H. Asorey for the LAGO Collaboration, {{LAGO: the Latin American Giant Observatory}}, \en Proc.
34th International Cosmic Ray Conference, PoS(ICRC2015)247, The Hague, The Netherlands, 2015

\item \years{2015}S. Dasso, A.M.\ Gulisano, J.J\  Masías-Meza and H. Asorey for the LAGO Collaboration, {{A Project to Install Water-Cherenkov Detectors in the Antarctic Peninsula as part of the LAGO Detection Network}}, \en Proc.
34th International Cosmic Ray Conference, PoS(ICRC2015)105, The Hague, The Netherlands, 2015

\item \years{2015}H. Asorey, S. Dasso, L.A.\ Núñez, Y. Perez, C. Sarmiento and M. Suárez-Durán for the LAGO Collaboration, {{The LAGO Space Weather Program: Directional Geomagnetic Effects, Background Fluence Calculations and Multi-Spectral Data Analysis}}, \en Proc.
34th International Cosmic Ray Conference, PoS(ICRC2015)142, The Hague, The Netherlands, 2015

\item \years{2015}H. Asorey, P. Miranda, A. Núñez-Castiñeyra, L.A.\ Núñez, J. Salinas, C. Sarmiento-Cano, R. Ticona and A. Velarde for the LAGO Collaboration, {{Analysis of Background Cosmic Ray Rate in the 2010--2012 Period from the LAGO-Chacaltaya Detectors}}, \en Proc.
34th International Cosmic Ray Conference, PoS(ICRC2015)414, The Hague, The Netherlands, 2015

\item \years{2015}H. Asorey, D. Cazar-Ramírez, R. Mayo-García, L.A.\ Núñez, M. Rodríguez-Pascual and L.A.\ Torres-Niño for the LAGO Collaboration, {{Data Accessibility, Reproducibility and Trustworthiness with LAGO Data Repositories}}, \en Proc.
34th International Cosmic Ray Conference, PoS(ICRC2015)672, The Hague, The Netherlands, 2015

\item \years{2014}S. Pinilla, H. Asorey, L.A.\ Núñez, {{Cosmic Rays Induced Background Radiation on Board of Commercial Flights}}, \en Proc.
X SILAFAE, Nuc.
Phys.
B Proc.
Supp., \ifeng accepted, \else aceptado,\fi\ Medellín, Colombia, 2014

\item \years{2014}H. Asorey for the LAGO Collaboration, {{The Latin American Giant Observatory}}, \en Proc.
X SILAFAE, Nuc.
Phys.
B Proc.
Supp., \ifeng accepted, \else aceptado,\fi\ Medellín, Colombia, 2014

\item \years{2014}S. Pinilla, H. Asorey, L.A.\ Núñez, {{Cosmic Rays Induced Background Radiation on Board of Commercial Flights}}, \en Proc.
X SILAFAE,  Nuc.
Part.
Phys.
Proc. {\textbf{267-269}} 418--420 (2015), Medellín, Colombia, 2014

\item \years{2014}R. Calderón, H. Asorey, L.A.\ Núñez for the LAGO Collaboration, {{Geant4 based simulation of the Water Cherenkov Detectors of the LAGO Project}}, \en Proc.
X SILAFAE, Nuc.
Part.
Phys.
Proc. {\textbf{267-269}} 424--426 (2015), Medellín, Colombia, 2014

\item \years{2014}A. Estupiñan, H. Asorey, L.A.\ Núñez, {{Implementing the De-thinning Method for High Energy Cosmic Rays Extensive Air Showers}}, \en Proc.
X SILAFAE, Nuc.
Part.
Phys.
Proc. {\textbf{267-269}} 421--423 (2015), Medellín, Colombia, 2014

\item \years{2014}H. Asorey for the LAGO Collaboration, {{The LAGO project}}, \ifeng invited talk in the \else charla invitada en el \fi III Astroparticle Physics Workshop: The future in South America, São Paulo, \ifeng Brazil\else Brasil\fi, 2014
  
\item \years{2014}H. Asorey for the LAGO Collaboration, {{The Latin American Giant Observatory}}, \en Proc.
X SILAFAE, Medellín, Colombia, 2014

\item \years{2014}H. Asorey for the LAGO Collaboration, {{The Latin American Giant Observatory (LAGO) project}}, \en Proc.
X COLAGE, Cusco, Perú, 2014

\item \years{2014}M. Suárez, H. Asorey and Núñez for the LAGO Collaboration, {{The rigidity cutoff calculation method for the Sites of the LAGO Project}}, \en Proc.
X COLAGE, Cusco, Perú, 2014

\item \years{2014}C. Sarmiento, H. Asorey and L. Núñez for the LAGO Collaboration, {{The GUANE Array of the LAGO Project: Studying Space Weather Phenomena from Ground Level}}, \en Proc.
X COLAGE, Cusco, Perú, 2014

\item \years{2014}H. Asorey and S. Dasso for the LAGO Collaboration, {{The LAGO Project Space Weather Program}}, \en 40th COSPAR Scientific Assembly, Moscú, Rusia, 2014

\item \years{2014}H. Asorey and S. Dasso. {{Astropartículas en LAGO}}, curso de Astropartículas y Física Heliosférica dictado en el marco del Encuentro Astropartículas 2014, Universidad San Francisco de Quito, Quito, Ecuador

\item \years{2013}H. Asorey and L. Núñez, {{Astronomy and Astrophysics in the Colombian Andes: the PAS Project}} \en Proc.
XIV Latin American Regional IAU Meeting LARIM2014, Florianopolis, \ifeng Brazil \else Brasil\fi, Rev.
Mex.
AA {\textbf{SC44}} 107 (2014)

\item \years{2013} H. Asorey, {{The Universidad Industrial de Santander New Introductory Physics Course}}, 
\ifeng
invited seminary at the
\else
seminario invitado en el
\fi
XXXI Encontro de Físicos do Norte e Nordeste, Campina Grande, Brasil, 4--8 Nov 2013.

\item \years{2013} H. Asorey, {{Muon Lifetime Measurements using the LAGO Water Cherenkov Detectors: a Tool to Introduce Particle Physics Concepts and Analysis Methods in Undergraduate Physics Courses}}, 
\ifeng
invited seminary at the
\else
seminario invitado en el
\fi
XXXI Encontro de Físicos do Norte e Nordeste, Campina Grande, Brasil, 4--8 Nov 2013.

\item \years{2013} H. Asorey, {{Astroparticles in Latin America}}, 
\ifeng
invited talk at the
\else
charla invitada en el 
\fi
XXXI Encontro de Físicos do Norte e Nordeste, Campina Grande, Brasil, 4--8 Nov 2013.

\item \years{2013}H. Asorey and L. Núñez, {{The ``Polo de Astronomía Social'' (PAS) Project: High Energy Astrophysics in the Colombian Andes}} \ifeng invited talk in the \else charla invitada en el \fi Workshop Astronomía en los Andes, Bogotá, Colombia, 2013.

\item \years{2013}H. Asorey for the LAGO Collaboration, \href{https://www.cbpf.br/~icrc2013/papers/icrc2013-0856.pdf}{The LAGO Solar Project}, \en Proc. 33th International Cosmic Ray Conference, Rio de Janeiro, Brazil, ICRC2013-0856 (2013)

\item \years{2013}H. Asorey, D. Melo {{et al.}}, \href{https://www.cbpf.br/~icrc2013/papers/icrc2013-1236.pdf}{Characterization of San Antonio de los Cobres for a Cherenkov telescope array in energy range from 20 GeV to 130 GeV}, \en Proc. 33 International Cosmic Ray Conference, Rio de Janeiro, Brazil, ICRC2013-1236 (2013)

\item \years{2012} H. Asorey, {{Astropartículas en América Latina}}, 
\ifeng
invited talk at the
\else
charla invitada en la 
\fi
Tercer Conferencia Colombiana de Astronomía y Astrofísica, COCOA2012, Bucaramanga, Colombia, 5--8 Nov 2012.

\item \years{2012} H. Asorey, M. Arribere, X. Bertou, M. Gómez Berisso, F. Sánchez,
{{Expected Backgrounds at the ANDES Underground Laboratory}}
\ifeng
plenary talk given at the
\else
charla plenaria dada en el
\fi
Third International Workshop for the Design of the ANDES Underground Laboratory, Valparaiso, Chile, 11--12 Jan 2012.

\item \years{2012}H. Asorey for the Pierre Auger Collaboration, {{Heliospheric
Modulation of Cosmic Rays Observed by the Pierre Auger Observatory and the LAGO
Project}}, 
\ifeng
parallel talk given at the 
\else
charla paralela en el 
\fi
4$^{\mathrm{th}}$ International Workshop of High Energy Physics in the LHC Era HEP2012, Valparaiso, Chile, 4--10 Jan 2012.

\item \years{2011}H. Asorey, {{Fermi Problem: Power developed at the eruption of the Puyehue-Cordón Caulle volcanic system in June 2011}}, 
\ifeng
talk given in the Physics Education Division during the 96$^{\mathrm{th}}$ National Meeting SUF-AFA2011 of the Argentinian Physics Association, Montevideo, Uruguay, 20--23 Sept 2011.
\else
charla de la división Educación en Física durante la 96$^{\mathrm{th}}$ Reunión Anual SUF-AFA2011 de la Asociación de Física Argentina, Montevideo, Uruguay, 20--23 Sept 2011.
\fi

\item \years{2011}H. Asorey, A. López Dávalos and A. Clúa, \href{https://dialnet.unirioja.es/servlet/articulo?codigo=4026852}{{Potencia de la Erupción del Volcán Puyehue como un Problema de Fermi}},
\ifeng
plenary talk given in the XVII Physics Education National Meeting APFA 2011 of the Argentinian Professors in Physics Association, Villa Giardino, Argentina, Oct 2011.
\else
charla plenaria presentada en la XVII Reunión Nacional de Educación en Física APFA 2011 de la Asociación de Profesores de Física de Argentina, Villa Giardino, Argentina, Oct 2011.
\fi
Rev.
Ens.
Fís. {\textbf{24}}(2), 49--54 (2011)

\item \years{2011}I. Allekotte, H. Arnaldi, H. Asorey, X. Bertou, M. Gómez Berisso,
M. Sofo Haro, {{Development of ultra-fast and ultra low power consumption
electronics in the Bariloche Particle and Radiation Detection Laboratory}},
\ifeng
póster presentation in the 96$^{\mathrm{th}}$ National Meeting SUF-AFA2011 of the Argentinian Physics Association, Montevideo, Uruguay, 20--23 Sept 2011.
\else
póster presentado en la 96$^{\mathrm{th}}$ Reunión Anual SUF-AFA2011 de la Asociación de Física Argentina, Montevideo, Uruguay, 20--23 Sept 2011.
\fi

\item \years{2011}H. Asorey[Pierre Auger Collaboration], {{Low energy radiation
measurements with the water Cherenkov detector array of the Pierre Auger
Observatory}}, \en Proc.
32nd International Cosmic Ray Conference, vol.
11
462--465, Beijing, China, 11--18 Ago 2011

\item \years{2011}The Pierre Auger Collaboration,
\href{http://arxiv.org/abs/1107.4805}{{The Pierre Auger Observatory III:
Other Astrophysical Observations}}, \en Proc.
32nd International Cosmic Ray
Conference, Beijing, China, 11--18 Ago 2011.

\item \years{2010}H. Asorey[Pierre Auger Collaboration],
\href{http://95rnf.afa.webfactional.com/tex\_files/Resumenes/DPyC/PyC\_6.pdf}{{The
infill array of the Pierre Auger Observatory}}, 
\ifeng
talk given in the Particle and Fields Division in the 95$^{\mathrm{th}}$ National Meeting AFA2010 of the Argentinian Physics Association, Malargüe, Argentina, 28 Sept--01 Oct 2010.
\else
charla dada en la división Partículas y Campos durante la 95$^{\mathrm{th}}$ Reunión Nacional AFA2010 de la Asociación de Física Argentina, Malargüe, Argentina, 28 Sept--01 Oct 2010.
\fi

\item \years{2010}H. Asorey, J. Castro, A. López Dávalos,
\href{http://95rnf.afa.webfactional.com/tex\_files/Resumenes/EF/asorey.pdf}{{Kepler,
Newton, Feynman}}, 
\ifeng
póster presentation in the 95$^{\mathrm{th}}$ National Meeting AFA2011 of the Argentinian Physics Association, Malargüe, Argentina, 28 Sept--01 Oct 2010.
\else
póster presentado en la 95$^{\mathrm{th}}$ Reunión Nacional AFA2010 de la Asociación de Física Argentina, Malargüe, Argentina, 28 Sept--01 Oct 2010.
\fi

\item \years{2010}H. Asorey[LAGO Collaboration], {{The Large Aperture Gamma Ray Burst Observatory (LAGO)}}, 
\ifeng
plenary talk in the 
\else
charla plenaria en el 
\fi
3$^{\mathrm{rd}}$ International Workshop of High Energy Physics in the LHC Era HEP2010, Valparaiso, Chile, 4--8 Jan 2010.

\item \years{2009}H. Asorey[Pierre Auger Collaboration], {{Cosmic Ray Solar
Modulation Studies at the Pierre Auger Observatory}}, \en Proc.
31st
International Cosmic Ray Conference, Lodz, Poland, 8--15 Jul 2009.

\item \years{2009}The Pierre Auger Collaboration,
\href{http://arxiv.org/abs/0906.2347}{{Astrophysical Sources of Cosmic
Rays and Related Measurements with the Pierre Auger Observatory}}, \en Proc.
31st International Cosmic Ray Conference, Lodz, Poland, 8--15 Jul 2009.

\item \years{2009}The LAGO Collaboration,\href{http://arxiv.org/abs/0906.0814}{{Operating Water Cherenkov Detectors in high altitude sites for the Large Aperture GRB Observatory}}, \en Proc.
31st International Cosmic Ray Conference, Lodz, Poland, 8--15 Jul 2009.

\item \years{2009}The LAGO Collaboration,
\href{http://arxiv.org/abs/0906.0816}{{The Large Aperture GRB
Observatory}}, \en Proc.
31st International Cosmic Ray Conference, Lodz,
Poland, 8--15 Jul 2009.

\item \years{2009}The LAGO Collaboration,\href{http://arxiv.org/abs/0906.0820}{{Water Cherenkov Detectors response to a Gamma Ray Burst in the Large Aperture GRB Observatory}}, \en Proc.
31st International Cosmic Ray Conference, Lodz, Poland, 8--15 Jul 2009.
\item \years{2009}H. Asorey[Pierre Auger Collaboration], {{The Acceptance of the
Pierre Auger Observatory}}, 
\ifeng
poster presentation in the VII Latin American Symposium of High Energy Physics SILAFAE 2009, San Carlos de Bariloche, Argentina, 14--21 Jan 2009.
\else
póster presentado en el VII Simposio Latinoamericano de Física de Altas Energías SILAFAE 2009, San Carlos de Bariloche, Argentina, 14--21 Jan 2009.
\fi

\item \years{2008}XVI Course of the ISCRA (International School of Cosmic Ray Astrophysics) 2008: ``Gamma Ray and Cosmic Ray Astrophysics: From below GeV to beyond EeV Energies'', Erice, Italia, Julio 2008

\item \years{2008}\ifeng Invited talk \else Charla invitada \fi ``Towards Cosmic ray Solar Modulation Studies'', University of Siegen, Siegen, Germany, 2008.

\item \years{2007}D. Allard { et al.}, {{Looking for the high energy component of GRBs at the Large Aperture GRB Observatory}}, in Proc.
30$^{\mathrm{th}}$ International Cosmic Ray Conference,  Mérida, Mexico, 3--11 Jul 2007.

\item \years{2007}IV Latin American School of Strings LASS 07, San Carlos de Bariloche, January 2007.

\item \years{2006}H. Asorey[Pierre Auger Collaboration], {{The Surface Detector Array of the Pierre Auger Observatory}}, 
\ifeng
parallel talk in the 
\else
charla paralela en el 
\fi
1$^{\mathrm{st}}$ International Workshop of High Energy Physics in the LHC Era HEP2006, Valparaiso, Chile, 12--17 Dec 2006.

\item \years{2006}D. Allard { et al.} [LAGO Collaboration], {{The Large Aperture GRB aperture}}, \en Proc.
of the Observational Astronomy in Argentina Workshop, Buenos Aires.

\item \years{2005}Third CERN-CLAF Latin American School Of High Energy Physics, CERN, Malargüe, Argentina.
Poster: ``Event Reconstruction using the Surface Detectors At UHECR Pierre Auger Observatory''

\item \years{2004}Sixth J. J. Giambiagi Winter School on Particle Physics, Facultad de Ciencias Exactas y Naturales, Universidad de Buenos Aires.
July 2004.

\item \years{2005-2015} 
\ifeng
Thirty seven technical and physics talks given at the Pierre Auger Collaboration meetings, Malargüe, Argentina.
\else
Treinta y siete charlas físicas y técnicas dadas en los Encuentros Anuales de la Colaboración Pierre Auger, Malargüe, Argentina.
\fi
\end{etaremune}
