\ifeng
\section*{Technical Works}
\subsection*{Technical Reports of Comisión Nacional de Energía Atómica}
\else
\section*{Trabajos Técnicos}
\subsection*{Reportes Técnicos de la Comisión Nacional de Energía Atómica}
\fi

\noindent
\begin{etaremune}

\item \years{2018} J. Lipovetzky, J. J. Blostein J. Irazoqui, D. Sanz, I. Sidelnik, H. Asorey, M. Gómez Berisso, H. Arnaldi, M. Pérez, F. Alcalde, M. Sofo-Haro, {\textit{Primera prueba fibras Wave Length Shifter en Radioterapia}}, Informe Técnico CNEA ITE-EN\_GIN-FN-007 Rev. 01, 2018.

\item \years{2017} I. Sidelnik, H. Asorey, N. Guarin, H. Arnaldi, J. Lipovetzky, J.J.\ Blostein, A. Mancilla, G. Anibal, M. Pérez, F. Alcalde, M. Sofo Haro, M. Gómez Berisso, {\textit{Diseño mejorado para la detección de neutrones mediante un detector Cherenkov en agua}} Informe Técnico CNEA, ITE-EN\_GIN-FN-003 Rev. 01, 2017.

\item \years{2015} I. Sidelnik, H. Asorey, J. J. Blostein, M. Gómez Berisso, H. Arnaldi, M. Sofo Haro, {\textit{Caracterización de un detector Cherenkov de agua en presencia de fuentes de neutrones de $^{241}$AmBe y $^{252}$Cf}}, Informe Técnico CNEA, ITE-EN\_GIN-FN-001, 2015.

\end{etaremune}

\ifeng
\subsection*{Internal notes of the Pierre Auger Observatory (GAP Notes)}

See \href{http://www.auger.org/admin-cgi-bin/woda/gap\_notes.pl/Search?search=asorey}{www.auger.org/admin/GAP\_Notes}.
\else
\subsection*{Notas internas del Observatorio Pierre Auger (GAP Notes)}

Ver \href{http://www.auger.org/admin-cgi-bin/woda/gap\_notes.pl/Search?search=asorey}{www.auger.org/admin/GAP\_Notes}.
\fi

\noindent
\begin{etaremune}

\item \years{2018} M. Suárez-Durán, H. Asorey, A. Taboada, S. Dasso, L. A. Núñez, {{Determination of the muonic component to the Forbush decrease of December 2006}}, GAP 2018--031

\item \years{2018} M. Suárez-Durán, H. Asorey, S. Dasso, L.A.\ Núñez, {{Assessing the Geomagnetic Field contribution during two Forbush Decreases: May 2005 and December 2006}}, GAP 2018--009

\item \years{2017} A. Valbuena, R. Ramos-Pollán, L.A.\ Núñez, H. Asorey, {{Exploiting Surface Detector Monitoring Data for Surface Temperature Prediction}}, GAP 2017--017

\item \years{2017} H. Asorey, {{Air density calculation for the new weather data sets of the Auger Observatory}}, GAP 2017--008

\item \years{2016} R. Ramos-Pollán, X. Bertou, L.A.\ Núñez, H. Asorey, {{Validating the usage of surface detector GPS position differentials to characterize ionospheric behavior}}, GAP 2016--070

\item \years{2016} H. Asorey, E. Roulet, {{The new weather data sets for the Auger Observatory Site}}, GAP 2016--049

\item \years{2015} H. Asorey, J. J. Blostein, M. Gómez Berisso, I. Sidelnik, {{Performance of a Water Cherenkov Detector by using different Neutron Sources}}, GAP 2015--030.

\item \years{2014} J. Macias, H. Asorey and S. Dasso, {{Long term analysis of the Scaler data: Identification of the Solar Cycle at Auger}}, GAP 2014--117.

\item \years{2013} H. Asorey, J. Blostein, M. Gómez Berisso, I. Sidelnik, {{Performance of a water Cherenkov detector by using a 241AmBe neutron source}}, GAP 2013--108.

\item \years{2012} H. Asorey, {{The Water Cherenkov Detectors of the Pierre Auger Observatory and their Application to the Study of Background Radiation}}, GAP 2012--131.

\item \years{2011} R. Ravignani, H. Asorey, D. Melo, G. De La Vega, A. Etchegoyen, A. Ferrero, R. F. Gamarra, B. García, M. Josebachuili, F. Sánchez, I. Sidelnik, A. Tapia, B. Wundheiler, {{Observation of the spectrum with the AMIGA infill}}, GAP 2011--010.

\item \years{2009}H. Asorey, I. Allekotte, X. Bertou, M. Gómez~Berisso, {{Acceptance of generalised Surface Detector Arrays from real data}}, GAP 2009--155.

\item \years{2009}H. Asorey, X. Bertou, D. Thomas, M. Mostafá, {{The OMG Hybrid Event}}, GAP 2011--154.

\item \years{2009}H. Asorey, I. Allekotte, X. Bertou, M. Gómez~Berisso, {{Determining the acceptance of the Pierre Auger Surface Detector with the Infill Array}}, GAP 2009--112.

\item \years{2009}I. Allekotte, H. Asorey, M. Gómez~Berisso, {{Improving the determination of the Auger Surface Detector Single Station Trigger Probability from real data}}, GAP 2009--019.

\item \years{2008}H. Asorey, X. Bertou, {{Determining the Dynamic Range needed for new Surface Detectors.}}, GAP 2008--117.

\item \years{2008}I. Allekotte, H. Asorey, X. Bertou, M. Gómez~Berisso, {{You thought you understood hexagons?}}, GAP 2008--114

\item \years{2008}S. Grebe, I. Allekotte, H. Asorey, X. Bertou, P. Buchholz, {{Robustness of the CDAS reconstruction algorithm.}}, GAP 2008--112.

\item \years{2008}H. Asorey, X. Bertou, {{First large timescale analysis of Auger SD scaler data: Towards cosmic ray Solar modulation studies.}}, GAP 2008--072.

\item \years{2007}H. Asorey, I. Allekotte, {{Towards a complete set of weather data.}}, GAP 2007--088.

\item \years{2006}H. Asorey, X. Bertou, E. Roulet, {{How to improve the SD arrival direction reconstruction by correcting the start-time of individual detectors.}}, GAP 2006--052.

\item \years{2005}H. Asorey, I. Allekotte, M. Gómez~Berisso, X. Bertou, {{Robustness of the angular reconstruction with the Surface Array of the Auger Observatory.}}, GAP 2005--107.

\item \years{2005}H. Asorey, I. Allekotte, M. Gómez~Berisso, X. Bertou, {{Robustness of the energy reconstruction with the Surface Array of the Auger Observatory.}}, GAP 2005--084.
\end{etaremune}
