\ifeng
\section*{Internal notes of the Pierre Auger Observatory (GAP Notes)}

See \href{http://www.auger.org/admin-cgi-bin/woda/gap\_notes.pl/Search?search=asorey}{www.auger.org/admin/GAP\_Notes}.
\else
\section*{Notas internas del Observatorio Pierre Auger (GAP Notes)}

Ver \href{http://www.auger.org/admin-cgi-bin/woda/gap\_notes.pl/Search?search=asorey}{www.auger.org/admin/GAP\_Notes}.
\fi

\noindent
\begin{etaremune}
\item \years{2014} J. Macias, H. Asorey and S. Dasso, {\emph{Long term analysis of the Scaler data: Identification of the Solar Cycle at Auger}}, GAP 2014-117.

\item \years{2013} H. Asorey, J. Blostein, M. Gómez Berisso, I. Sidelnik, {\emph{Performance of a water Cherenkov detector by using a 241AmBe neutron source}}, GAP 2013-108.

\item \years{2011} R. Ravignani, H. Asorey, D. Melo, G. De La Vega, A. Etchegoyen, A. Ferrero, R. F. Gamarra, B. García, M. Josebachuili, F. Sánchez, I. Sidelnik, A. Tapia, B. Wundheiler, {\emph{Observation of the spectrum with the AMIGA infill}}, GAP 2011-010.

\item \years{2009}H. Asorey, I. Allekotte, X. Bertou, M. Gómez~Berisso, {\emph{Acceptance of generalised Surface Detector Arrays from real data}}, GAP 2009-155.

\item \years{2009}H. Asorey, X. Bertou, D. Thomas, M. Mostafá, {\emph{The OMG Hybrid Event}}, GAP 2011-154.

\item \years{2009}H. Asorey, I. Allekotte, X. Bertou, M. Gómez~Berisso, {\emph{Determining the acceptance of the Pierre Auger Surface Detector with the Infill Array}}, GAP 2009-112.

\item \years{2009}I. Allekotte, H. Asorey, M. Gómez~Berisso, {\emph{Improving the determination of the Auger Surface Detector Single Station Trigger Probability from real data}}, GAP 2009-019.

\item \years{2008}H. Asorey, X. Bertou, {\emph{Determining the Dynamic Range needed for new Surface Detectors.}}, GAP 2008-117.

\item \years{2008}I. Allekotte, H. Asorey, X. Bertou, M. Gómez~Berisso, {\emph{You thought you understood hexagons?}}, GAP 2008-114

\item \years{2008}S. Grebe, I. Allekotte, H. Asorey, X. Bertou, P. Buchholz, {\emph{Robustness of the CDAS reconstruction algorithm.}}, GAP 2008-112.

\item \years{2008}H. Asorey, X. Bertou, {\emph{First large timescale analysis of Auger SD scaler data: Towards cosmic ray Solar modulation studies.}}, GAP 2008-072.

\item \years{2007}H. Asorey, I. Allekotte, {\emph{Towards a complete set of weather data.}}, GAP 2007-088.

\item \years{2006}H. Asorey, X. Bertou, E. Roulet, {\emph{How to improve the SD arrival direction reconstruction by correcting the start-time of individual detectors.}}, GAP 2006-052.

\item \years{2005}H. Asorey, I. Allekotte, M. Gómez~Berisso, X. Bertou, {\emph{Robustness of the angular reconstruction with the Surface Array of the Auger Observatory.}}, GAP 2005-107.

\item \years{2005}H. Asorey, I. Allekotte, M. Gómez~Berisso, X. Bertou, {\emph{Robustness of the energy reconstruction with the Surface Array of the Auger Observatory.}}, GAP 2005-084.
\end{etaremune}
