\ifeng
\subsection*{Selected Works}
\noindent
% During the development of my work within the Pierre Auger Observatory, I have been acting as the Physics coordinator and responsible of one of the full author list papers of the Pierre Auger Collaboration (The Pierre Auger Collaboration, JINST {\bf 6} P01003--P01020 (2011)), using the surface detector in a novel way, developed during my Ph.D. thesis, as a tool to study transient solar phenomena and heliospheric modulation of galactic cosmic rays flux.

This list is a personal selection of the published works I have been directly involved:

\else
\subsection*{Trabajos seleccionados}
\noindent
% Durante el desarrollo de mi trabajo en el marco del Observatorio Pierre Auger, tuve la oportunidad de actuar como Coordinador de Física y responsable directo de la publicación de uno de los trabajos publicados por toda la Colaboración Auger (The Pierre Auger Collaboration, JINST {\bf 6} P01003--P01020 (2011)), que consiste en el uso del arreglo de detectores de superficie para el estudio de fenómenos heliosféricos mediante la modulación del flujo de rayos cósmicos galácticos. Este uso novedoso del arreglo SD fue desarrollado como parte de mi tesis de doctorado en Física.

La lista mostrada a continuación corresponde a una selección personal de los trabajos publicados en los cuales estuve directamente involucrado:
\fi

\noindent
\begin{etaremune}

\item \years{2017}I. Sidelnik \& H. Asorey, {\emph{LAGO: the Latin American Giant Observatory}}, NIM-A \ifeng in press \else en prensa,\fi 2017 \href{http://arxiv.org/abs/1703.05337}{arXiv:1703.05337}[astro-ph.IM]

\item \years{2017} I. Sidelnik, H. Asorey, J. J. Blostein \& M. Gómez Berisso, {\emph{Neutron Detection Using a Water Cherenkov Detector with Pure Water and a Single PMT}}, NIM-A \ifeng in press \else en prensa,\fi 2017

\item \years{2017}The Pierre Auger Collaboration, \href{https://doi.org/10.1088/1748-0221/12/03/P03002}{\emph{Muon counting using silicon photomultipliers in the AMIGA detector of the Pierre Auger observatory}} JINST {\bf 12} P03002 (2017) \href{http://arxiv.org/abs/1703.06193}{arXiv:1703.06193}[astro-ph.IM]

\item \years{2017}The Pierre Auger Collaboration, \href{https://doi.org/10.1088/1748-0221/12/02/P02006}{\emph{Impact of atmospheric effects on the energy reconstruction of air showers observed by the surface detectors of the Pierre Auger Observatory}} JINST {\bf 12} P02006 (2017) \href{http://arxiv.org/abs/1702.02835}{arXiv:1702.02835}[astro-ph.IM]

\item \years{2016} The Pierre Auger Collaboration, {\emph{The Pierre Auger Observatory Upgrade-Preliminary Design Report}}, \href{http://arxiv.org/abs/1604.03637}{arXiv:1604.03637}[astro-ph.IM]
	
\item \years{2015}H. Asorey for the LAGO Collaboration, {\emph{LAGO: the Latin American Giant Observatory}}, \en Proc. 34th International Cosmic Ray Conference, PoS(ICRC2015)247, The Hague, The Netherlands, 2015

\item \years{2016} H. Asorey, R. Mayo-García, L.A. Núñez, M. Rodríguez-Pascual, A. J. Rubio-Montero, M. Suarez Durán, \& L.A. Torres-Niño for the LAGO Collaboration, {\emph{\href{http://dx.doi.org/10.1109/CCGrid.2016.110}{The Latin American Giant Observatory: a successful collaboration in Latin America based on Cosmic Rays and computer science domains}}}, \en Proc. 2016 16th IEEE/ACM International Symposium on Cluster, Cloud and Grid Computing (CCGrid), IEEE Proccedings, pp 707-711, Cartagena, Colombia, 2016, \href{http://arxiv.org/abs/1605.09295}{arXiv:1605.09295}[astro-ph.IM]

\item \years{2015} I. Sidelnik, H. Asorey, J. J. Blostein, M. Gómez Berisso, H. Arnaldi, M. Sofo Haro, {\emph{Detección de Neutrones mediante efecto Cherenkov en Agua}}, Actas de la Reunión Anual de la Asociación Argentina de Tecnología Nuclear (2015).

\item \years{2015}H. Asorey \& L. A. Núñez, {\emph{Astroparticle Physics at Eastern Colombia}}, \en Proc. César Lattes Meeting, \ifeng accepted \else aceptado,\fi Niterói, Brazil, 2015 \href{http://arxiv.org/abs/1510.01305}{arXiv:1510.01305}[astro-ph.IM]

\item \years{2015}H. Asorey for the LAGO Collaboration, {\emph{LAGO: the Latin American Giant Observatory}}, \en Proc. 34th International Cosmic Ray Conference, PoS(ICRC2015)247, The Hague, The Netherlands, 2015

\item \years{2015}S. Dasso, A.M. Gulisano, J.J. Masías-Meza \& H. Asorey for the LAGO Collaboration, {\emph{A Project to Install Water-Cherenkov Detectors in the Antarctic Peninsula as part of the LAGO Detection Network}}, \en Proc. 34th International Cosmic Ray Conference, PoS(ICRC2015)105, The Hague, The Netherlands, 2015

\item \years{2015}H. Asorey, S. Dasso, L.A. Núñez, Y. Perez, C. Sarmiento \& M. Suárez-Durán for the LAGO Collaboration, {\emph{The LAGO Space Weather Program: Directional Geomagnetic Effects, Background Fluence Calculations and Multi-Spectral Data Analysis}}, \en Proc. 34th International Cosmic Ray Conference, PoS(ICRC2015)142, The Hague, The Netherlands, 2015

\item \years{2015}H. Asorey, P. Miranda, A. Núñez-Castiñeyra, L.A. Núñez, J. Salinas, C. Sarmiento-Cano, R. Ticona \& A. Velarde for the LAGO Collaboration, {\emph{Analysis of Background Cosmic Ray Rate in the 2010-2012 Period from the LAGO-Chacaltaya Detectors}}, \en Proc. 34th International Cosmic Ray Conference, PoS(ICRC2015)414, The Hague, The Netherlands, 2015

\item \years{2015}H. Asorey, D. Cazar-Ramírez, R. Mayo-García, L.A. Núñez, M. Rodríguez-Pascual \& L.A. Torres-Niño for the LAGO Collaboration, {\emph{Data Accessibility, Reproducibility and Trustworthiness with LAGO Data Repositories}}, \en Proc. 34th International Cosmic Ray Conference, PoS(ICRC2015)672, The Hague, The Netherlands, 2015

\item \years{2014}H. Asorey for the LAGO Collaboration, {\emph{The Latin American Giant Observatory}}, \en Proc. X SILAFAE, Nuc. Phys. B Proc. Supp., \ifeng submitted, \else enviado,\fi\ Medellín, Colombia, 2014

\item \years{2014}S. Pinilla, H. Asorey, L.A. Núñez, {\emph{Cosmic Rays Induced Background Radiation on Board of Commercial Flights}}, \en Proc. X SILAFAE, Nuc. Phys. B Proc. Supp., \ifeng accepted, \else aceptado,\fi\ Medellín, Colombia, 2014

\item \years{2014}H. Asorey for the LAGO Collaboration, {\emph{The Latin American Giant Observatory}}, \en Proc. X SILAFAE, Nuc. Phys. B Proc. Supp., \ifeng accepted, \else aceptado,\fi\ Medellín, Colombia, 2014

\item \years{2014}S. Pinilla, H. Asorey, L.A. Núñez, {\emph{Cosmic Rays Induced Background Radiation on Board of Commercial Flights}}, \en Proc. X SILAFAE,  Nuc. Part. Phys. Proc. {\bf{267-269}} 418-420 (2015), Medellín, Colombia, 2014

\item \years{2014}R. Calderón, H. Asorey, L.A. Núñez for the LAGO Collaboration, {\emph{Geant4 based simulation of the Water Cherenkov Detectors of the LAGO Project}}, \en Proc. X SILAFAE, Nuc. Part. Phys. Proc. {\bf{267-269}} 424-426 (2015), Medellín, Colombia, 2014

\item \years{2014}The Pierre Auger Collaboration, \href{http://dx.doi.org/10.1088/0004-637X/794/2/172}{\emph{earches for Large-scale Anisotropy in the Arrival Directions of Cosmic Rays Detected above Energy of 1019 eV at the Pierre Auger Observatory and the Telescope Array}} ApJ {\bf{794}}(2), 172 (2014)

\item \years{2014}H. Asorey for the LAGO Collaboration, {\emph{The Latin American Giant Observatory (LAGO) project}}, \en Proc. X COLAGE, Adv. Space Res. \ifeng submitted, \else enviado,\fi  Cusco, Perú, 2014

\item \years{2014}M. Suárez, H. Asorey \& Núñez for the LAGO Collaboration, {\emph{The rigidity cutoff calculation method for the Sites of the LAGO Project}}, \en Proc. X COLAGE, Adv. Space Res. \ifeng submitted, \else enviado,\fi  Cusco, Perú, 2014

\item \years{2014}C. Sarmiento, H. Asorey \& L. Núñez for the LAGO Collaboration, {\emph{The GUANE Array of the LAGO Project: Studying Space Weather Phenomena from Ground Level}}, \en Proc. X COLAGE, Adv. Space Res. \ifeng submitted, \else enviado,\fi  Cusco, Perú, 2014

\item \years{2014}H. Asorey \& S. Dasso for the LAGO Collaboration, {\emph{The LAGO Project Space Weather Program}}, \en Proc. 40th COSPAR Scientific Assembly, Adv. Space Res. \ifeng submitted, \else enviado,\fi  Moscú, Rusia, 2014

\item \years{2014}H. Asorey, J.I. Castro \& A. López Dávalos, \href{http://www.revistas.unc.edu.ar/index.php/revistaEF/article/view/9512}{\emph{Una deducción analítica simple de la hodógrafa para el problema de Kepler}}, Rev. Ens. Fís. {\bf{26}}(1), 63-73 (2014).

\item \years{2013}H. Asorey \& L. Núñez, {\emph{Astronomy and Astrophysics in the Colombian Andes: the PAS Project}} \en Proc. XIV Latin American Regional IAU Meeting LARIM2014, Rev. Mex. AA Conf. Series, \ifeng in press, \else en prensa,\fi  Florianopolis, Brazil, 2013

\item \years{2013}H. Asorey for the LAGO Collaboration, {\emph{The LAGO Solar Project}}, \en Proc. 33 International Cosmic Ray Conference, \ifeng in press, \else en prensa,\fi  Rio de Janeiro, Brazil, 2013

\item \years{2013}H. Asorey, D. Melo {\emph{et al.}}, {\emph{Characterization of San Antonio de los Cobres for a Cherenkov telescope array in energy range from 20 GeV to 130 GeV}}, \en Proc. 33 International Cosmic Ray Conference, \ifeng in press, \else en prensa,\fi  Rio de Janeiro, Brazil, 2013

\item \years{2012}S. Dasso \& H. Asorey, for the Pierre Auger Collaboration,
\href{http://dx.doi.org/10.1016/j.asr.2011.12.028}{\emph{ The scaler mode in
the Pierre Auger Observatory to study heliospheric modulation of cosmic rays
}}, Adv. Space Res. {\bf{49}} (11), 1563--1569 (2012)

\item \years{2012} H. Asorey, M. Arribere, X. Bertou, M. Gómez Berisso, F. Sánchez,
{\emph{Expected Backgrounds at the ANDES Underground Laboratory}}
\ifeng
plenary talk given at the
\else 
charla plenaria dada en el
\fi
Third International Workshop for the Design of the ANDES Underground Laboratory, Valparaiso, Chile, 11--12 Jan 2012.

\item \years{2011}The Pierre Auger Collaboration,
\href{http://dx.doi.org/10.1088/1748-0221/6/01/P01003}{\emph{The Pierre Auger
Observatory Scaler Mode for the Study of the Modulation of Galactic Cosmic Rays
due to Solar Activity}}, JINST {\bf 6} P01003--
P01020 (2011).
\ifeng $^*${\bf{Coordinator}} \else $^*${\bf{Coordinador}} \fi

\item \years{2011} The Pierre Auger Collaboration, 
\href{http://dx.doi.org/10.1016/j.astropartphys.2011.08.001}{\emph{The Lateral
Trigger Probability function for UHE Cosmic Rays Showers detected by the Pierre
Auger Observatory}}, Astropart. Phys. {\bf{35}} (5), 266--276 (2011)

\item \years{2011}H. Asorey \& A. López Dávalos, {\emph{Fermi Problem: Power
developed at the eruption of the Puyehue-Cordón Caulle volcanic system in June
2011}}, \href{http://arxiv.org/abs/1109.1165}{arXiv:1109.1165v1}[physics.ed-ph]. \ifeng
Selected as the best \href{http://arxiv.org}{arXiv} paper of September 2011 by the
\else
Seleccionado como el mejor trabajo enviado al \href{http://arxiv.org}{arXiv} durante Setiembre del 2011 por el blog 
\fi
\href{http://www.technologyreview.com/blog/arxiv/27140/}{M.I.T. Technology
Review Physics arXiv Blog}, (2011)

\item \years{2011}H. Asorey, A. López Dávalos \& A. Clúa, {\emph{Potencia de la Erupción del Volcán Puyehue como un Problema de Fermi}}, Rev. Ens. Fís. {\bf{24}}(2), 49-54 (2011)

\item \years{2011}I. Allekotte, H. Arnaldi, H. Asorey, X. Bertou, M. Gómez Berisso, \& M. Sofo Haro, {\emph{Development of ultra-fast and ultra low power consumption electronics in the Bariloche Particle and Radiation Detection Laboratory}},
\ifeng
poster presentation in the 96$^{\mathrm{th}}$ National Reunion SUF-AFA2011 of the Argentinian Physics Association, Montevideo, Uruguay, 20--23 Sept 2011.
\else
poster presentado en la 96$^{\mathrm{th}}$ Reunión Nacional SUF-AFA2011 de la Asociación Argentina de Física, Montevideo, Uruguay, 20--23 Sept 2011.
\fi

\item \years{2011}H. Asorey[Pierre Auger Collaboration], {\emph{Low energy radiation
measurements with the water Cherenkov detector array of the Pierre Auger
Observatory}}, \en Proc. 32 International Cosmic Ray Conference, vol. 11
462--465, Beijing, China, 11--18 Ago 2011

\item \years{2011}The Pierre Auger Collaboration,
\href{http://dx.doi.org/10.1016/j.astropartphys.2010.12.007}{\emph{Search for
First Harmonic Modulation in the Right Ascension Distribution of Cosmic Rays
Detected at the Pierre Auger Observatory}}, Astropart. Phys. {\bf 34} 627--639
(2011)

\item \years{2010}J. Bl\"umer \& The Pierre Auger Collaboration,
\href{http://dx.doi.org/10.1088/1367-2630/12/3/035001}{\emph{The Northern Site
of the Pierre Auger Observatory}}, Journal of Physics {\bf 12} (3) 035001

\item \years{2010}The Pierre Auger Collaboration,
\href{http://dx.doi.org/10.1016/j.physletb.2010.02.013}{\emph{Measurement of
the energy spectrum of cosmic rays above $10^{18}$ eV using the Pierre Auger
Observatory}}, Phys. Lett. {\bf B685} 239--246 (2010),\\
\href{http://arxiv.org/abs/1002.1975}{arXiv:1002.1975v1}[astro-ph.HE]

\item \years{2010}The Pierre Auger Collaboration,
\href{http://dx.doi.org/10.1016/j.nima.2009.11.018}{\emph{Trigger and Aperture
of the Surface Detector Array of the Pierre Auger Observatory}}, NIM {\bf A613}
29--39, (2010)

\item \years{2010}H. Asorey[LAGO Collaboration], {\emph{The Large Aperture Gamma Ray
Burst Observatory (LAGO)}}, plenary talk in the 3$^{\mathrm{rd}}$ International Workshop of
High Energy Physics in the LHC Era HEP2010, Valparaiso, Chile, 4--8 Jan 2010.

\item \years{2009}H. Asorey[Pierre Auger Collaboration], {\emph{Cosmic Ray Solar
Modulation Studies at the Pierre Auger Observatory}}, \en Proc. 31th
International Cosmic Ray Conference, Lodz, Poland, 8--15 Jul 2009.

\item \years{2009} The Pierre Auger Collaboration,
\href{http://dx.doi.org/10.1016/j.astropartphys.2009.06.004}{\emph{Atmospheric
effects on extensive air showers observed with the Surface Detector of the
Pierre Auger Observatory}}, Astropart. Phys. {\bf 32}, 89--99, (2009),
\href{http://arxiv.org/abs/0906.5497/}{arXiv:0906.5497v2}[astro-ph.IM]

\item \years{2008}The Pierre Auger Collaboration,
\href{http://dx.doi.org/10.1103/PhysRevLett.101.061101}{\emph{Observation of
the Suppression of the Flux of Cosmic Rays above $4\times10^{19}$\,eV.}}, PRL
{\bf 101} 061101 (2008)

\item \years{2008}The Pierre Auger Collaboration,
\href{http://dx.doi.org/10.1016/j.astropartphys.2008.01.003}{\emph{Upper limit
on the cosmic-ray photon flux above 10$^{19}$\,eV using the surface detector of
the Pierre Auger Observatory.}}, Astropart. Phys. {\bf 29} 243--256 (2008)

\item \years{2008}The Pierre Auger Collaboration,
\href{http://dx.doi.org/10.1016/j.astropartphys.2008.01.002}{\emph{Correlation
of the highest-energy cosmic rays with the positions of nearby active galactic
nuclei.}}, Astropart. Phys. {\bf 29} 188--204 (2008)

\item \years{2007}The Pierre Auger Collaboration,
\href{http://dx.doi.org/10.1126/science.1151124}{\emph{Correlation of the
highest energy cosmic rays with nearby extragalactic objects.}}, Science {\bf
318} 939--943 (2007)

\item \years{2008}D. Allard {\emph et al.} [LAGO Collaboration],
\href{http://dx.doi.org/10.1016/j.nima.2008.07.041}{\emph{Use of
water-Cherenkov detectors to detect Gamma Ray Bursts at the Large Aperture GRB
Observatory (LAGO)}}, NIM {\bf A595} 70--72 (2008)

\item \years{2007}D. Allard {\emph et al.} [LAGO Collaboration], {\emph{Looking for
the high energy component of GRBs at the Large Aperture GRB Observatory}}, \en
Proc. 30$^{\mathrm{th}}$ International Cosmic Ray Conference,  Mérida, Mexico, 3-11 Jul
2007.

\item \years{2007}The Pierre Auger Collaboration,
\href{http://dx.doi.org/10.1016/j.astropartphys.2006.11.002}{\emph{Anisotropy
studies around the galactic centre at EeV energies with the Auger
Observatory.}},  Astropart. Phys. {\bf 27} 244--253 (2007)

\item \years{2006}D. Allard {\emph et al.} [LAGO Collaboration], {\emph{The Large
Aperture GRB aperture}}, \en Proc. of the Observational Astronomy in Argentina
Workshop, Buenos Aires.

\end{etaremune}
