\ifeng
\subsection*{Participation \& presentations at Schools \& Conferences}
\else
\subsection*{Participación \& presentaciones en Escuelas \& Conferencias}
\fi
\noindent
\begin{etaremune}

%%% DE AQUI PARA ABAJO ESTAN EN EL SIGEVA %%%%

\item \years{2017} H. Asorey, A. Balaguera-Rojas, L. A. Núñez, J. D. Sanabria-Gómez, C. Sarmiento-Cano, M. Súarez-Duran, M. Valencia-Otero, \& A. Vesga-Ramírez, \href{}{\emph{Astroparticle Techniques: Colombia active volcano candidates for Muon Telescope}} \en Proc. XV Latin American Regional IAU Meeting LARIM2016, Cartagena, Colombia, Rev. Mex. AA, \ifeng in press \else en prensa \fi (2017) \href{http://arxiv.org/abs/1704.04967}{arXiv:1704.04967}[physics.geo-ph]

\item \years{2017}H. Asorey, A. Martínez-Méndez, L. A. Núñez \& A. Valbuena-Delgado, \href{}{\emph{LAGO Distributed Network Of Data Repositories}} \en Proc. XV Latin American Regional IAU Meeting LARIM2016, Cartagena, Colombia, Rev. Mex. AA, \ifeng in press \else en prensa \fi (2017) \href{http://arxiv.org/abs/1704.03885}{arXiv:1704.03885}[cs.DL]

\item \years{2017}H. Asorey, L. Núñez, C. Y. Pérez Arias, S. Pinilla, F. Quiñonez \& M. Suárez-Durán, \href{}{\emph{Astroparticle Techniques: Simulating Cosmic Rays induced Background Radiation on Aircrafts}} \en Proc. XV Latin American Regional IAU Meeting LARIM2016, Cartagena, Colombia, Rev. Mex. AA, \ifeng in press \else en prensa \fi (2017) \href{http://arxiv.org/abs/1704.03419}{arXiv:1704.03419}[physics.space-ph]

\item \years{2017} H. Asorey, \href{http://ifa.uv.cl/rayoscosmicos/}{\emph{Instructor invitado para la Primera Escuela Chilena de de Rayos Cósmicos - IV Escuela ``Astropartículas en LAGO''}}, con el curso \href{https://github.com/lagoproject/astroparticulas}{\emph{``Física de Astropartículas: física, simulaciones y análisis de datos''}}, Universidad de Valparaiso y Unisersidad de La Serena, Valparaiso y La Serena, Chile (2017).

\item \years{2016} H. Asorey, \href{https://fisica.cab.cnea.gov.ar/jab2016/}{\emph{Instructor invitado para la Escuela Jose Antonio Balseiro 2016: `` Nuevas Tendencias de Investigación en Física Médica''}}, con el curso \href{ https://github.com/asoreyh/intro-nuclear-fisica-medica }{\emph{``Curso de Introducción a Física de Partículas, Nuclear, Aceleradores y Detectores''}}, Instituto Balseiro, San Carlos de Bariloche, Argentina (2016).

\item \years{2016} H. Asorey, R. Mayo-García, L.A. Núñez, M. Rodríguez-Pascual, A. J. Rubio-Montero, M. Suarez Durán, \& L.A. Torres-Niño for the LAGO Collaboration, {\emph{\href{http://dx.doi.org/10.1109/CCGrid.2016.110}{The Latin American Giant Observatory: a successful collaboration in Latin America based on Cosmic Rays and computer science domains}}}, \en Proc. 2016 16th IEEE/ACM International Symposium on Cluster, Cloud and Grid Computing (CCGrid), IEEE Proccedings, pp 707-711, Cartagena, Colombia, 2016, \href{http://arxiv.org/abs/1605.09295}{arXiv:1605.09295}[astro-ph.IM] 

\item \years{2015} I. Sidelnik, H. Asorey, J. J. Blostein, M. Gómez Berisso, H. Arnaldi, M. Sofo Haro, {\emph{Detección de Neutrones mediante efecto Cherenkov en Agua}}, Actas de la Reunión Anual de la Asociación Argentina de Tecnología Nuclear (2015).

\item \years{2015}H. Asorey \& L. A. Núñez, {\emph{Astroparticle Physics at Eastern Colombia}}, \en Proc. César Lattes Meeting, \ifeng accepted \else aceptado,\fi Niterói, Brazil, 2015 \href{http://arxiv.org/abs/1510.01305}{arXiv:1510.01305}[astro-ph.IM]

\item \years{2015}H. Asorey for the LAGO Collaboration, {\emph{LAGO: the Latin American Giant Observatory}}, \en Proc. 34th International Cosmic Ray Conference, PoS(ICRC2015)247, The Hague, The Netherlands, 2015

\item \years{2015}S. Dasso, A.M. Gulisano, J.J. Masías-Meza \& H. Asorey for the LAGO Collaboration, {\emph{A Project to Install Water-Cherenkov Detectors in the Antarctic Peninsula as part of the LAGO Detection Network}}, \en Proc. 34th International Cosmic Ray Conference, PoS(ICRC2015)105, The Hague, The Netherlands, 2015

\item \years{2015}H. Asorey, S. Dasso, L.A. Núñez, Y. Perez, C. Sarmiento \& M. Suárez-Durán for the LAGO Collaboration, {\emph{The LAGO Space Weather Program: Directional Geomagnetic Effects, Background Fluence Calculations and Multi-Spectral Data Analysis}}, \en Proc. 34th International Cosmic Ray Conference, PoS(ICRC2015)142, The Hague, The Netherlands, 2015

\item \years{2015}H. Asorey, P. Miranda, A. Núñez-Castiñeyra, L.A. Núñez, J. Salinas, C. Sarmiento-Cano, R. Ticona \& A. Velarde for the LAGO Collaboration, {\emph{Analysis of Background Cosmic Ray Rate in the 2010-2012 Period from the LAGO-Chacaltaya Detectors}}, \en Proc. 34th International Cosmic Ray Conference, PoS(ICRC2015)414, The Hague, The Netherlands, 2015

\item \years{2015}H. Asorey, D. Cazar-Ramírez, R. Mayo-García, L.A. Núñez, M. Rodríguez-Pascual \& L.A. Torres-Niño for the LAGO Collaboration, {\emph{Data Accessibility, Reproducibility and Trustworthiness with LAGO Data Repositories}}, \en Proc. 34th International Cosmic Ray Conference, PoS(ICRC2015)672, The Hague, The Netherlands, 2015

\item \years{2014}S. Pinilla, H. Asorey, L.A. Núñez, {\emph{Cosmic Rays Induced Background Radiation on Board of Commercial Flights}}, \en Proc. X SILAFAE, Nuc. Phys. B Proc. Supp., \ifeng accepted, \else aceptado,\fi\ Medellín, Colombia, 2014

\item \years{2014}H. Asorey for the LAGO Collaboration, {\emph{The Latin American Giant Observatory}}, \en Proc. X SILAFAE, Nuc. Phys. B Proc. Supp., \ifeng accepted, \else aceptado,\fi\ Medellín, Colombia, 2014

\item \years{2014}S. Pinilla, H. Asorey, L.A. Núñez, {\emph{Cosmic Rays Induced Background Radiation on Board of Commercial Flights}}, \en Proc. X SILAFAE,  Nuc. Part. Phys. Proc. {\bf{267-269}} 418-420 (2015), Medellín, Colombia, 2014

\item \years{2014}R. Calderón, H. Asorey, L.A. Núñez for the LAGO Collaboration, {\emph{Geant4 based simulation of the Water Cherenkov Detectors of the LAGO Project}}, \en Proc. X SILAFAE, Nuc. Part. Phys. Proc. {\bf{267-269}} 424-426 (2015), Medellín, Colombia, 2014

\item \years{2014}A. Estupiñan, H. Asorey, L.A. Núñez, {\emph{Implementing the De-thinning Method for High Energy Cosmic Rays Extensive Air Showers}}, \en Proc. X SILAFAE, Nuc. Part. Phys. Proc. {\bf{267-269}} 421-423 (2015), Medellín, Colombia, 2014

\item \years{2014}H. Asorey for the LAGO Collaboration, {\emph{The LAGO project}}, \ifeng invited talk in the \else charla invitada en el \fi III Astroparticle Physics Workshop: The future in South America, Sao Paulo, \ifeng Brazil\else Brasil\fi, 2014
  
\item \years{2014}H. Asorey for the LAGO Collaboration, {\emph{The Latin American Giant Observatory}}, \en Proc. X SILAFAE, to appear in Nuc. Phys. B Proc. Supp. \ifeng submitted, \else enviado,\fi  Medellín, Colombia, 2014

\item \years{2014}H. Asorey for the LAGO Collaboration, {\emph{The Latin American Giant Observatory (LAGO) project}}, \en Proc. X COLAGE, Adv. Space Res. \ifeng submitted, \else enviado,\fi  Cusco, Perú, 2014

\item \years{2014}M. Suárez, H. Asorey \& Núñez for the LAGO Collaboration, {\emph{The rigidity cutoff calculation method for the Sites of the LAGO Project}}, \en Proc. X COLAGE, Adv. Space Res. \ifeng submitted, \else enviado,\fi  Cusco, Perú, 2014

\item \years{2014}C. Sarmiento, H. Asorey \& L. Núñez for the LAGO Collaboration, {\emph{The GUANE Array of the LAGO Project: Studying Space Weather Phenomena from Ground Level}}, \en Proc. X COLAGE, Adv. Space Res. \ifeng submitted, \else enviado,\fi  Cusco, Perú, 2014

\item \years{2014}H. Asorey \& S. Dasso for the LAGO Collaboration, {\emph{The LAGO Project Space Weather Program}}, \en 40th COSPAR Scientific Assembly, Moscú, Rusia, 2014

\item \years{2014}H. Asorey \& S. Dasso. {\emph{Astropartículas en LAGO}}, curso de Astropartículas y Física Heliosférica dictado en el marco del Encuentro Astropartículas 2014, Universidad San Francisco de Quito, Quito, Ecuador

\item \years{2013}H. Asorey \& L. Núñez, {\emph{Astronomy and Astrophysics in the Colombian Andes: the PAS Project}} \en Proc. XIV Latin American Regional IAU Meeting LARIM2014, Florianopolis, \ifeng Brazil \else Brasil\fi, Rev. Mex. AA {\bf{SC44}} 107 (2014)

\item \years{2013} H. Asorey, {\emph{The Universidad Industrial de Santander New Introductory Physics Course}}, 
\ifeng
invited seminary at the
\else
seminario invitado en el
\fi
XXXI Encontro de Físicos do Norte e Nordeste, Campina Grande, Brasil, 4--8 Nov 2013.

\item \years{2013} H. Asorey, {\emph{Muon Lifetime Measurements using the LAGO Water Cherenkov Detectors: a Tool to Introduce Particle Physics Concepts and Analysis Methods in Undergraduate Physics Courses}}, 
\ifeng
invited seminary at the
\else
seminario invitado en el
\fi
XXXI Encontro de Físicos do Norte e Nordeste, Campina Grande, Brasil, 4--8 Nov 2013.

\item \years{2013} H. Asorey, {\emph{Astroparticles in Latin America}}, 
\ifeng
invited talk at the
\else
charla invitada en el 
\fi
XXXI Encontro de Físicos do Norte e Nordeste, Campina Grande, Brasil, 4--8 Nov 2013.

\item \years{2013}H. Asorey \& L. Núñez, {\emph{The ``Polo de Astronomía Social'' (PAS) Project: High Energy Astrophysics in the Colombian Andes}} \ifeng invited talk in the \else charla invitada en el \fi Workshop Astronomía en los Andes, Bogotá, Colombia, 2013.
    
\item \years{2013}H. Asorey for the LAGO Collaboration, {\emph{The LAGO Solar Project}}, \en Proc. 33 International Cosmic Ray Conference, \ifeng in press, \else en prensa,\fi  Rio de Janeiro, Brazil, 2013

\item \years{2013}H. Asorey, D. Melo {\emph{et al.}}, {\emph{Characterization of San Antonio de los Cobres for a Cherenkov telescope array in energy range from 20 GeV to 130 GeV}}, \en Proc. 33 International Cosmic Ray Conference, \ifeng in press, \else en prensa,\fi  Rio de Janeiro, Brazil, 2013

\item \years{2012} H. Asorey, {\emph{Astropartículas en América Latina}}, 
\ifeng
invited talk at the
\else
charla invitada en la 
\fi
Tercer Conferencia Colombiana de Astronomía y Astrofísica, COCOA2012, Bucaramanga, Colombia, 5--8 Nov 2012.

\item \years{2012} H. Asorey, M. Arribere, X. Bertou, M. Gómez Berisso, F. Sánchez,
{\emph{Expected Backgrounds at the ANDES Underground Laboratory}}
\ifeng
plenary talk given at the
\else
charla plenaria dada en el
\fi
Third International Workshop for the Design of the ANDES Underground Laboratory, Valparaiso, Chile, 11--12 Jan 2012.

\item \years{2012}H. Asorey [Pierre Auger Collaboration], {\emph{Heliospheric
Modulation of Cosmic Rays Observed by the Pierre Auger Observatory and the LAGO
Project}}, 
\ifeng
parallel talk given at the 
\else
charla paralela en el 
\fi
4$^{\mathrm{th}}$ International Workshop of High Energy Physics in the LHC Era HEP2012, Valparaiso, Chile, 4--10 Jan 2012.

\item \years{2011}H. Asorey, {\emph{Fermi Problem: Power developed at the eruption of the Puyehue-Cordón Caulle volcanic system in June 2011}}, 
\ifeng
talk given in the Physics Education Division during the 96$^{\mathrm{th}}$ National Meeting SUF-AFA2011 of the Argentinian Physics Association, Montevideo, Uruguay, 20--23 Sept 2011.
\else
charla de la división Educación en Física durante la 96$^{\mathrm{th}}$ Reunión Anual SUF-AFA2011 de la Asociación de Física Argentina, Montevideo, Uruguay, 20--23 Sept 2011.
\fi

\item \years{2011}H. Asorey, A. López Dávalos \& A. Clúa, {\emph{Potencia de la Erupción del Volcán Puyehue como un Problema de Fermi}},
\ifeng
plenary talk given in the XVII Physics Education National Meeting APFA 2011 of the Argentinian Professors in Physics Association, Villa Giardino, Argentina, Oct 2011.
\else
charla plenaria presentada en la XVII Reunión Nacional de Educación en Física APFA 2011 de la Asociación de Profesores de Física de Argentina, Villa Giardino, Argentina, Oct 2011.
\fi
Rev. Ens. Fís. {\bf{24}}(2), 49-54 (2011)

\item \years{2011}I. Allekotte, H. Arnaldi, H. Asorey, X. Bertou, M. Gómez Berisso,
M. Sofo Haro, {\emph{Development of ultra fast and ultra low power consumption
electronics in the Bariloche Particle and Radiation Detection Laboratory}},
\ifeng
póster presentation in the 96$^{\mathrm{th}}$ National Meeting SUF-AFA2011 of the Argentinian Physics Association, Montevideo, Uruguay, 20--23 Sept 2011.
\else
póster presentado en la 96$^{\mathrm{th}}$ Reunión Anual SUF-AFA2011 de la Asociación de Física Argentina, Montevideo, Uruguay, 20--23 Sept 2011.
\fi

\item \years{2011}H. Asorey[Pierre Auger Collaboration], {\emph{Low energy radiation
measurements with the water Cherenkov detector array of the Pierre Auger
Observatory}}, \en Proc. 32th International Cosmic Ray Conference, vol. 11
462--465, Beijing, China, 11--18 Ago 2011

\item \years{2011}The Pierre Auger Collaboration,
\href{http://arxiv.org/abs/1107.4805}{\emph{The Pierre Auger Observatory III:
Other Astrophysical Observations}}, \en Proc. 32th International Cosmic Ray
Conference, Beijing, China, 11--18 Ago 2011.

\item \years{2010}H. Asorey[Pierre Auger Collaboration],
\href{http://95rnf.afa.webfactional.com/tex\_files/Resumenes/DPyC/PyC\_6.pdf}{\emph{The
infill array of the Pierre Auger Observatory}}, 
\ifeng
talk given in the Particle and Fields Division in the 95$^{\mathrm{th}}$ National Meeting AFA2010 of the Argentinian Physics Association, Malargüe, Argentina, 28 Sept--01 Oct 2010.
\else
charla dada en la división Partículas y Campos durante la 95$^{\mathrm{th}}$ Reunión Nacional AFA2010 de la Asociación de Física Argentina, Malargüe, Argentina, 28 Sept--01 Oct 2010.
\fi

\item \years{2010}H. Asorey, J. Castro, A. López Dávalos,
\href{http://95rnf.afa.webfactional.com/tex\_files/Resumenes/EF/asorey.pdf}{\emph{Kepler,
Newton, Feynman}}, 
\ifeng
póster presentation in the 95$^{\mathrm{th}}$ National Meeting AFA2011 of the Argentinian Physics Association, Malargüe, Argentina, 28 Sept--01 Oct 2010.
\else
póster presentado en la 95$^{\mathrm{th}}$ Reunión Nacional AFA2010 de la Asociación de Física Argentina, Malargüe, Argentina, 28 Sept--01 Oct 2010.
\fi

\item \years{2010}H. Asorey[LAGO Collaboration], {\emph{The Large Aperture Gamma Ray Burst Observatory (LAGO)}}, 
\ifeng
plenary talk in the 
\else
charla plenaria en el 
\fi
3$^{\mathrm{rd}}$ International Workshop of High Energy Physics in the LHC Era HEP2010, Valparaiso, Chile, 4--8 Jan 2010.

\item \years{2009}H. Asorey[Pierre Auger Collaboration], {\emph{Cosmic Ray Solar
Modulation Studies at the Pierre Auger Observatory}}, \en Proc. 31th
International Cosmic Ray Conference, Lodz, Poland, 8--15 Jul 2009.

\item \years{2009}The Pierre Auger Collaboration,
\href{http://arxiv.org/abs/0906.2347}{\emph{Astrophysical Sources of Cosmic
Rays and Related Measurements with the Pierre Auger Observatory}}, \en Proc.
31th International Cosmic Ray Conference, Lodz, Poland, 8--15 Jul 2009.

\item \years{2009}The LAGO Collaboration,\href{http://arxiv.org/abs/0906.0814}{\emph{Operating Water Cherenkov Detectors in high altitude sites for the Large Aperture GRB Observatory}}, \en Proc. 31th International Cosmic Ray Conference, Lodz, Poland, 8--15 Jul 2009.

\item \years{2009}The LAGO Collaboration,
\href{http://arxiv.org/abs/0906.0816}{\emph{The Large Aperture GRB
Observatory}}, \en Proc. 31th International Cosmic Ray Conference, Lodz,
Poland, 8--15 Jul 2009.

\item \years{2009}The LAGO Collaboration,\href{http://arxiv.org/abs/0906.0820}{\emph{Water Cherenkov Detectors response to a Gamma Ray Burst in the Large Aperture GRB Observatory}}, \en Proc. 31th International Cosmic Ray Conference, Lodz, Poland, 8--15 Jul 2009.
\item \years{2009}H. Asorey[Pierre Auger Collaboration], {\emph{The Acceptance of the
Pierre Auger Observatory}}, 
\ifeng
poster presentation in the VII Latinamerican Symposium of High Energy Physics SILAFAE 2009, San Carlos de Bariloche, Argentina, 14-21 Jan 2009.
\else
póster presentado en el VII Simposio Lationamericano de Física de Altas Energías SILAFAE 2009, San Carlos de Bariloche, Argentina, 14-21 Jan 2009.
\fi

\item \years{2008}XVI Course of the ISCRA (International School of Cosmic Ray Astrophysics) 2008: ``Gamma Ray and Cosmic Ray Astrophysics: From below GeV to beyond EeV Energies'', Erice, Italia, Julio 2008

\item \years{2008}\ifeng Invited talk \else Charla invitada \fi ``Towards Cosmic ray Solar Modulation Studies'', University of Siegen, Siegen, Germany, 2008.

\item \years{2007}D. Allard {\emph et al.} [LAGO Collaboration], {\emph{Looking for the high energy component of GRBs at the Large Aperture GRB Observatory}}, in Proc. 30$^{\mathrm{th}}$ International Cosmic Ray Conference,  Mérida, Mexico, 3-11 Jul 2007.

\item \years{2007}IV Latin American School of Strings LASS 07, San Carlos de Bariloche, January 2007.

\item \years{2006}H. Asorey[Pierre Auger Collaboration], {\emph{The Surface Detector Array of the Pierre Auger Observatory}}, 
\ifeng
parallel talk in the 
\else
charla paralela en el 
\fi
1$^{\mathrm{st}}$ International Workshop of High Energy Physics in the LHC Era HEP2006, Valparaiso, Chile, 12--17 Dec 2006.

\item \years{2006}D. Allard {\emph et al.} [LAGO Collaboration], {\emph{The Large Aperture GRB aperture}}, \en Proc. of the Observational Astronomy in Argentina Workshop, Buenos Aires.

\item \years{2005}Third CERN-CLAF Latin American School Of High Energy Physics, CERN, Malargüe, Argentina. Poster: ``Event Reconstruction using the Surface Detectors At UHECR Pierre Auger Observatory''

\item \years{2004}Sixth J. J. Giambiagi Winter School on Particle Physics, Facultad de Ciencias Exactas y Naturales, Universidad de Buenos Aires. July 2004.

\item \years{2005-2015} 
\ifeng
Thirty seven technical and physics talks given at the Pierre Auger Collaboration meetings, Malargüe, Argentina.
\else
Treinta y siete charlas físicas y técnicas dadas en los Encuentros Anuales de la Colaboración Pierre Auger, Malargüe, Argentina.
\fi
\end{etaremune}
